Should geophysicists use gravity anomaly or gravity disturbance?

### 2018-05-16 manuscript/letter.tex
Changes to definition of anomaly and disturbance
Simplified some of the text and added some missing italics.
Removed the P subscript from the gravity anomaly because it is not
defined on the point P (which is where the disturbance is defined).
The anomaly can't be defined on a point in 3D space, as we comment right
below that. So it's best to just say Delta g or Delta g(lambda, phi).

Added a part about not being able to upward continue Delta g because
it's not harmonic. This was implied by a sentence below saying that we
can upcontinue the disturbance bc it is harmonic.

Rephrased the part ab

\newcommand{\versor}[1]{\hat{\mathbf{#1}}}
\renewcommand{\vector}[1]{\vec{\mathbf{#1}}}

@@

\section{Relationship between gravity disturbance and gravity anomaly}

@@

The difference between the magnitudes of gravity vector
$g_{P} = \| \vector{g}_{P} \|$ and the normal gravity vector
$\gamma_{P} = \| \vector{\gamma}_{P} \|$, at the
same point $P$, is called \textit{gravity disturbance}
\citep{heiskanen-moritz1967, hofmann-wellenhof-moritz2005}
and can be represented as follows:

@@

Notice that the gravity disturbance $\delta g_{P}$ is not equivalent
to the magnitude of the gravity disturbance vector
$\delta \vector{g}_{P}$ \citep{barthelmes2013, sanso_sideris2013}.

On the other hand, the \textit{gravity anomaly vector} at $P$
is the difference between the gravity
vector at a point $Q^{\prime}$ on the Geoid (a particular
equipotential surface of the gravity potential) and the normal
gravity vector at a point $Q$ on the ellipsoid surface, both at the
same geodetic latitude and longitude (Fig. \ref{fig:surfaces}) as in
\begin{equation}
\Delta \vector{g}_{P} = \vector{g}_{Q^{\prime}} - \vector{\gamma}_{Q} .
\label{eq:gravity-anomaly-vector}
\end{equation}
Similarly to the gravity disturbance expression (eq.
\ref{eq:gravity-disturbance}), the gravity anomaly is given by
\begin{equation}
\Delta g_{P} = g_{Q^{\prime}} - \gamma_{Q} ,
\label{eq:gravity-anomaly}
\end{equation}
where $g_{Q^{\prime} } = \| \vector{g}_{Q^{\prime}} \|$ is
the magnitude of the gravity vector $\vector{g}_{Q}$ on the Geoid,
at $Q^{\prime}$, and $\gamma_{Q} = \| \vector{\gamma}_{Q} \|$ is the
magnitude of the normal gravity vector $\vector{\gamma}_{Q}$
on the reference ellipsoid, at the point $Q$ (Fig. \ref{fig:surfaces}).
As properly pointed out by \citet{barthelmes2013} the gravity anomaly,
by definition, depends on
longitude and latitude only and is not a function of height.
Because the gravity is on the Geoid and the normal gravity
is on reference ellipsoid, the gravity anomaly $\Delta g_{P}$
(eq. \ref{eq:gravity-anomaly}) is not a purely gravitational effect
due to the gravity sources, but rather a combination of gravitational
and centrifugal effects. Consequently, its upward continuation,
for example, could not be rigorously done.

However, many authors in the literature have computed the upward
continuation of gravity anomalies. All these authors have
implicitly considered that the gravity anomaly is an approximation of
the gravity disturbance, which in turn can be represented by a
harmonic function and can then being upward continued.

>>>>

\newcommand{\versor}[1]{\hat{\mitbf{#1}}}
\renewcommand{\vector}[1]{\vec{\mitbf{#1}}}

@@

\section{gravity disturbance and gravity anomaly}

@@

The difference between the magnitudes of the gravity vector
$g_{P} = \| \vector{g}_{P} \|$ and the normal gravity vector
$\gamma_{P} = \| \vector{\gamma}_{P} \|$,
at the same point $P$, is the \textit{gravity disturbance}
\citep{heiskanen-moritz1967, hofmann-wellenhof-moritz2005}:

@@

\noindent
Notice that $\delta g_{P}$ is not equivalent
to the magnitude of the gravity disturbance vector
$\delta \vector{g}_{P}$ \citep{barthelmes2013, sanso_sideris2013}.

The \textit{gravity anomaly vector}
is the difference between the gravity
vector at a point $Q^{\prime}$ on the geoid
(a particular equipotential surface of the gravity potential)
and the normal gravity vector at a point $Q$ on the surface of the ellipsoid,
both located at the same geodetic latitude and longitude
(Fig. \ref{fig:surfaces}):

\begin{equation}
\Delta \vector{g} = \vector{g}_{Q^{\prime}} - \vector{\gamma}_{Q} .
\label{eq:gravity-anomaly-vector}
\end{equation}

Similarly to the gravity disturbance (eq. \ref{eq:gravity-disturbance}),
the \textit{gravity anomaly} is given by

\begin{equation}
\Delta g = g_{Q^{\prime}} - \gamma_{Q} ,
\label{eq:gravity-anomaly}
\end{equation}

\noindent
where $g_{Q^{\prime}}$ is the magnitude of the gravity vector on the geoid,
and $\gamma_{Q}$ is the magnitude of the normal gravity vector
on the reference ellipsoid (Fig. \ref{fig:surfaces}).

The gravity anomaly is not defined at a particular point.
Instead, as properly pointed out by \citet{barthelmes2013},
it depends only on longitude and latitude and is not a function of height.
Because gravity and normal gravity are located at different points,
the gravity anomaly is a combination of gravitational and centrifugal effects,
rather than purely gravitational effects like the gravity disturbance.
Consequently, its upward continuation, for example, cannot be rigorously done
because it is not a harmonic function.
However, upward continuation of gravity anomalies is commonly seen in the
literature.
In doing so, an implicit assumption is being made that the gravity anomaly is
an approximation of the gravity disturbance,
which in turn can be represented by a harmonic function and can be upward
continued.
